Slavnov products and KP tau functions

### 2025-04-17 draft.tex
add more details on the calculation of the BA function

Let us define the components
\begin{equation}
  \begin{split}
    \widetilde{\mathcal{K}}_{kj} = &
    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
    + \delta_{nj} F_k(\lambda) \\
    & = \sum_{\ell = 1}^n  \widetilde{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
    + \delta_{nj} F_k(\lambda) \\
  \end{split}
\end{equation}
where
\begin{equation}
  \widetilde{\Omega}_{k\ell}
  = \frac{1}{z_\ell} \frac{\widetilde{\mathcal{Y}}_k(\lambda, z_\ell)}{z_\ell - v_k}
  = \frac{(\lambda z_\ell -1)}{\lambda z_\ell} {\Omega}_{k\ell} 
\; , \qquad 
 F_k(\lambda) = (-1)^n \frac{\widetilde{\mathcal{Y}}_k(\lambda; 0)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
\end{equation}
We conclude that we are basically adding a constant vector
\(\bm{F} = (F_1, \dots , F_n)\) to the \(n\)-th line of a matrix with components...

>>>>

Let us define the components
\begin{equation}
  \begin{split}
    \widetilde{\mathcal{K}}_{kj} = &
    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
    + \delta_{nj} F_k(\lambda) \\
    & = \sum_{\ell = 1}^n  \widetilde{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
    + F_k(\lambda)\delta_{nj}  \\
  \end{split}
\end{equation}
where
\begin{equation}
  \widetilde{\Omega}_{k\ell}
  = \frac{1}{z_\ell} \frac{\widetilde{\mathcal{Y}}_k(\lambda, z_\ell)}{z_\ell - v_k}
  = \frac{(\lambda z_\ell -1)}{\lambda z_\ell} {\Omega}_{k\ell} 
\; , \qquad 
 F_k(\lambda) = (-1)^n \frac{\widetilde{\mathcal{Y}}_k(\lambda; 0)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
\end{equation}

In order to simplify our analysis, let us define one more matrix
\(\widehat{\mathcal{K}}\) by its components
\begin{equation}
    \widehat{\mathcal{K}}_{kj} = 
    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}\; .
\end{equation}
We conclude that \(\widetilde{\mathcal{K}}\) can be obtained from 
\(\widehat{\mathcal{K}}\) by adding to each component of the \(n\)-th row
the corresponding component of the vector \(\bm{F} = (F_1, \dots , F_n)\). 
Let us write this operation as 
\begin{equation}
  \widetilde{\mathcal{K}} = \widehat{\mathcal{K}} + \bm{F}_{[\rightarrow n-row]}\; ,
\end{equation}
